---
title: "Univariate Homework"
author: "Morgan Lattomus"
date: "2/1/2000"
output:
  html_document: default
  word_document: default
  pdf_document: default
---


```{r}
trees <- read.csv('https://raw.githubusercontent.com/dmcglinn/quant_methods/gh-pages/data/treedata_subset.csv')
```

1. Carry out an exploratory analysis using the tree dataset. Metadata for the tree study can be found here. Specifically, I would like you to develop and compare models for species cover for a habitat generalist Acer rubrum (Red maple) and a habitat specialist Abies fraseri (Frasier fir). Because this dataset includes both continuous and discrete explanatory variables use the function Anova in the packages car as such

```{r loading dependencies}
#install.packages('car')
library(car)
```


```{r}
sp_cov = with(trees, tapply(cover, list(plotID, spcode), 
  function(x) round(mean(x))))
sp_cov = ifelse(is.na(sp_cov), 0, sp_cov)
sp_cov = data.frame(plotID = row.names(sp_cov), sp_cov)
```

```{r}
cols_to_select = c('elev', 'tci', 'streamdist', 'disturb', 'beers')
env = aggregate(trees[ , cols_to_select], by = list(trees$plotID), 
                function(x) x[1])
names(env)[1] = 'plotID'
```

```{r}
site_dat = merge(sp_cov, env, by='plotID')
```

```{r}
abies = site_dat[ , c('ABIEFRA', cols_to_select)]
acer  = site_dat[ , c('ACERRUB', cols_to_select)]
names(abies)[1] = 'cover'
names(acer)[1] = 'cover'
```

```{r}
my_mod <- lm(abies$cover ~ acer$cover, data = trees) 
Anova(my_mod, type = 3)
```

```{r}
summary(my_mod)
```

```{r}
par(mfrow=c(1,2))
plot(abies, acer ~ cover, data = trees, xlab = 'Tree Species',ylab = 'Cover')
abline(my_mod)
```
Additional Questions
- How well does the exploratory model appear to explain cover? 

  Explains it well, a lot of the values between the summary and the Anova were very similar, implying that 
  
- Which explanatory variables are the most important?

- Do model diagnostics indicate any problems with violations of OLS assumptions?

- Are you able to explain variance in one species better than another, why might this be the case?


2. Re-examine your solutions to the question above but from the perspective of a General Linear Model (GLM) with a Poisson error term. #graphically

```{r}
acer_poi = glm(cover ~ tci + elev + streamdist + disturb + beers, data = trees,
              family='poisson')
acer_poi
```

```{r}
abies_poi = glm(cover ~ tci + elev + streamdist + disturb + beers , data = trees,
              family='poisson')
abies_poi
```

```{r}
psuedo_r2 = function(glm_mod) {
  1 - glm_mod$deviance / glm_mod$null.deviance
  }
psuedo_r2
```

3. Provide a plain English summary of what you have found and what conclusions we can take away from your analysis?